%\documentclass{sensys-proc}
%\documentclass{sig-alternate-ipsn13}
\documentclass{acm_proc_article-sp}
%\documentclass{sig-alternate}
\usepackage{subcaption}
\usepackage{epstopdf}
%\usepackage{times}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{comment}
%\usepackage[ruled,linesnumbered]{algorithm2e}
\usepackage[ruled]{algorithm2e}
%\usepackage{algorithmic}
%\usepackage{algpseudocode}
\usepackage[yyyymmdd, hhmmss]{datetime}
%\pagestyle{fancy}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand{\mt}{\mathsf{T}}

\begin{document}
\conferenceinfo{BuildSys'13,} {November 14--15, 2013, Rome, Italy} 
\CopyrightYear{2013} 
\crdata{978-1-4503-2431-1/13/11} 
\clubpenalty=10000 
\widowpenalty = 10000

\title{Sensor Type Classification\\ with Transfer Learning Across Buildings
}
\numberofauthors{1} 
\author{
\alignauthor
Dezhi Hong$^1$,  Hongning Wang$^1$,  Kamin Whitehouse$^1$, Jorge Ortiz$^2$\\
	\affaddr{$^1$Department of Computer Science, University of Virginia, VA USA}\\
	\affaddr{$^2$IBM T.J. Watson Research Center, Yorktown Heights, NY USA}\\
	\email{\{hong, hongning, whitehouse\}@virginia.edu, jjortiz@us.ibm.com}
}

\maketitle
\begin{abstract}
%Buildings consume a large amount of the energy produced in the United States and much of it is wasted. 
Many sensors/meters are deployed in commercial buildings to monitor and optimize their performance.  
However, because sensor metadata is inconsistent across buildings, software-based
solutions are \emph{tightly coupled} to the sensor metadata conventions (i.e. schemas and naming) for each building. 
% -- used for sensors in each
% specific building.  It impossible to create widely deployable software-based solutions that run across
% buildings without significant integration effort.
% , sometimes even missing, which makes scalable, meaningful large-scale applitions in 
% buildings impractical.
Running the same software across buildings requires significant integration effort.

% Metadata normalization is critical for scaling the software deployment process.  It allows us to
% \emph{decouple} building-specific conventions from the code written for building applications.
% In this context, normalization is non-trivial and requires a we believe it requires suite of solutions.  We assert that one such component of 
% that suite should differentiate sensor feeds by \emph{type}.  For example, we should be able to differentiate between sensors measuring 
% temperature and sensors measuring pressure.  In addition, we should be able to use what we learn from one building and apply
% it to another.

Metadata normalization is critical for scaling the deployment process and allows us to \emph{decouple} building-specific conventions 
from the code written for building applications.  It also allows us to deal with \emph{missing} metadata.  One important aspect of 
normalization is to differentiate sensors by the \emph{type}
of phenomena being observed.
In this paper, we propose a general, simple, yet effective classification scheme to differentiate sensors in buildings by type.
We perform ensemble learning on data collected from over 2000 sensor streams in two buildings.
Our approach is able to achieve more than 92\% accuracy for classification within buildings and more than 82\% accuracy for across buildings. 
We also introduce a method for identifying potential misclassified streams.  This is important because it allows us to identify opportunities to 
attain more input from experts -- input that could help improve classification accuracy when ground truth is unavailable.  We show that
 % which can be used to help improve classification accuracy when the ground truth labels are not available. 
by adjusting a threshold value we are able to identify at least 30\% of the misclassified instances.
\end{abstract}

\category{C.3}{Special-Purpose And Application-Based Systems}{Real-time and embedded systems}
\terms{Performance, Experimentation, Verification}
\keywords{Building, Sensor Type, Transfer Learning}

% \newpage
\input{intro}

\input{feature}

\input{method}

\input{evaluation}

%\input{discussion}

\input{relatedwork}

\input{conclusion}

%\section{Acknowledgements}
%Thanks to our shepherd, Kin Cheong Sou, and the anonymous reviewers for helpful comments. Thanks to Albert Goto, for making the first author's stay at UC Berkeley comfortable. Sincere gratitude goes to Kamin and David, for letting this collaboration happen. This work was partly funded by the NSF grants EFRI-1038271 and CPS-1239552.
\bibliographystyle{abbrv}
\small
\bibliography{buildsys}

%\balancecolumns
\end{document}
